Clicks and Cliques

### 2018-12-28 papersoul.Rnw
sampling weights in race diversity

soul %>% select(race, CCEGRP2, CCE, QSB,PROJWT, YEAR) %>% 
  filter(!is.na(PROJWT), YEAR!=2010)  %>% 
  mutate(wt = PROJWT/2) %>% 
  svydesign(ids=~1, strata=~QSB, weights=~wt, data=.) %>% 
  svyby(~race+CCEGRP2+CCE,~QSB, design = ., svymean,keep.var=FALSE, na.rm=T) %>%
  gather(race, prop, contains('race')) %>% 
  group_by(QSB) %>% 
  summarise(
    statistic.CCEGRP2Attached = first(statistic.CCEGRP2Attached),
    diver  = -sum( prop[prop > 0]*log(prop[prop>0]) )
  ) %>% 
  ggplot(aes(x = diver, y = logit(statistic.CCEGRP2Attached))) +
  geom_point(size = I(5)) + 
  geom_smooth(se = FALSE, method = 'lm', size = I(1)) +
  theme(axis.text.y = element_text( size = I(10)) ) + 
  labs( y = 'Proportion of Attach (logit scale)', x = 'Race diversity index')

>>>>

soul %>% select(race, CCEGRP2, CCE, QSB,WEIGHT, YEAR) %>% 
  filter(!is.na(WEIGHT), YEAR!=2010)  %>% 
  mutate(wt = WEIGHT/2) %>% 
  svydesign(ids=~1, strata=~QSB, weights=~wt, data=.) %>% 
  svyby(~race+CCEGRP2+CCE,~QSB, design = ., svymean,keep.var=FALSE, na.rm=T) %>%
  gather(race, prop, contains('race')) %>% 
  group_by(QSB) %>% 
  summarise(
    statistic.CCEGRP2Attached = first(statistic.CCEGRP2Attached),
    diver  = -sum( prop[prop > 0]*log(prop[prop>0]) )
  ) %>% 
  ggplot(aes(x = diver, y = logit(statistic.CCEGRP2Attached))) +
  geom_point(size = I(5)) + 
  geom_smooth(se = FALSE, method = 'lm', size = I(1)) +
  theme(axis.text.y = element_text( size = I(10)), aspect.ratio = 1 ) + 
  labs( y = 'Proportion of Attach (logit scale)', x = 'Race diversity index')
